---
title: "04-analysis.Rmd"
output: pdf_document
---
```{r, echo=FALSE}
library(xtable)
library(ggplot2)
load("../../data/mse_table.RData")
load("../../data/coef_table.RData")
load(file="../../data/ridge.RData")
load(file="../../data/plsr.RData")
load(file="../../data/lm.RData")
load(file="../../data/coef_table.RData")
```

#Results

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Now that we have a better understanding of each of these regression methods, lets look at the data in order to see how each regression performed: 
<table border = 1>
<tr>
<td>
```{r results='asis', echo=FALSE}
  library(xtable)
  print(xtable(mse, caption="Mean Squared Error For Each Regression",digits=6) ,caption.placement='top', comment=F)
```

</td>

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Lets take a look at how the estimated regression coefficients differ for each regression: 

<table border = 1>
<tr>
<td>
```{r results='asis', echo=FALSE}
  print(xtable(betas, caption="Beta Coefficients for Each Regression"),    caption.placement='top', comment=F, scalebox='.65')
```

</td>
\begin{figure}[h]
\caption{Coefficient Plot}
\centering
\includegraphics[width=250pt, height=255pt]{../../images/coefficient_plot.png}
\end{figure}


